Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-04-07 04_paper/Draft2.Rmd
adding new 'figure'

```{r}
library(tidyverse)
library(kableExtra)
dt <- read_csv(
  paste0(str_remove(getwd(), "/04_paper"), 
         "/01_data/final_data/final_data_imputed.csv")
)
```

@@

```{r, include=FALSE}
load(
  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
)
reg.tab1 <- reg.tab
cat(reg.tab1)
```

@@

>>>>

```{r}
library(tidyverse)
library(kableExtra)
library()
dt <- read_csv(
  paste0(str_remove(getwd(), "/04_paper"), 
         "/01_data/final_data/final_data_imputed.csv")
)
```

@@

```{r, include=FALSE}
load(
  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
)
load(
  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/model_list1.R") 
)
reg.tab1 <- reg.tab
cat(reg.tab1)
```

@@

```{r}
coef_table <- map_dfr(
  model_list,
  ~ tidy(coeftest(.x))
) %>%
  filter(
    str_detect(term, "count") | 
      str_detect(term, "visits")
  ) %>%
  mutate(
    conf.low = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error,
    term = rep(c("Coverage", "Visits"), len = n())
  ) %>%
  select(term, estimate, conf.low, conf.high)
tibble(
  "1" = coef_table$term[1:2],
  "2" = coef_table$estimate[1:2],
  "3" = " ",
  "4" = coef_table$estimate[3:4],
  "5" = " ",
  "6" = coef_table$estimate[5:6],
  "7" = " ",
  "8" = coef_table$estimate[7:8],
  "9" = " ",
  "10" = coef_table$estimate[9:10],
  "11" = " ",
  "12" = coef_table$estimate[11:12],
  "13" = " "
) %>% 
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  kable("latex", booktabs = T,
        caption = "Model Estimates",
        col.names = c(
          " ", rep(c("Est.", "95% CI"), len = 12)
        )) %>%
  kable_classic(full_width = F) %>%
  column_spec(
    3, image = spec_pointrange(
      x = coef_table$estimate[1:2],
      xmin = coef_table$conf.low[1:2],
      xmax = coef_table$conf.high[1:2],
      vline = 0
    )
  ) %>%
  column_spec(
    5, image = spec_pointrange(
      x = coef_table$estimate[3:4],
      xmin = coef_table$conf.low[3:4],
      xmax = coef_table$conf.high[3:4],
      vline = 0
    )
  ) %>%
  column_spec(
    7, image = spec_pointrange(
      x = coef_table$estimate[5:6],
      xmin = coef_table$conf.low[5:6],
      xmax = coef_table$conf.high[5:6],
      vline = 0,
      lim = c(0, max(coef_table$conf.high[5:6]))
    )
  ) %>%
  column_spec(
    9, image = spec_pointrange(
      x = coef_table$estimate[7:8],
      xmin = coef_table$conf.low[7:8],
      xmax = coef_table$conf.high[7:8],
      vline = 0
    )
  )%>%
  column_spec(
    11, image = spec_pointrange(
      x = coef_table$estimate[9:10],
      xmin = coef_table$conf.low[9:10],
      xmax = coef_table$conf.high[9:10],
      vline = 0
    )
  ) %>%
  column_spec(
    13, image = spec_pointrange(
      x = coef_table$estimate[11:12],
      xmin = coef_table$conf.low[11:12],
      xmax = coef_table$conf.high[11:12],
      vline = 0
    )
  ) %>%
  add_header_above(
    c(
      " " = 1,
      "Linear" = 2,
      "Tobit" = 2,
      "Selection" = 2,
      "Level" = 2,
      "IV Lag" = 2,
      "IV Lewbel" = 2
    )
  )%>% cat()

```
